My title

### 2023-03-14 outputs/paper/paper.qmd
In "paper.qmd", replaced all "geom_point()" with "geom_col()" to make our graphs bar charts instead of scatterplots.

# use tidyverse-style code to pivot and summarise the data 
mean_age |> ggplot(aes(x = variable, y = value)) + 
  geom_point() +
  theme(axis.text.x = element_text(angle = 45,hjust=1), 
        axis.line = element_line(colour = "black"),
        title = element_text(size = 12)) +
  labs(
    x = "Age Group",
    y = "Average Internet Usage Hours"
  )

@@

# use tidyverse-style code to pivot and summarise the data 
mean_sex |> ggplot(aes(x = variable, y = value)) + 
  geom_point() +
  theme(axis.text.x = element_text(angle = 45,hjust=1), 
        axis.line = element_line(colour = "black"),
        title = element_text(size = 12)) +
  labs(
    x = "Sex",
    y = "Average Internet Usage Hours"
  )

@@

# use tidyverse-style code to pivot and summarise the data 
mean_race |> ggplot(aes(x = variable, y = value)) + 
  geom_point() +
  theme(axis.text.x = element_text(angle = 45,hjust=1), 
        axis.line = element_line(colour = "black"),
        title = element_text(size = 12)) +
  labs(
    x = "Race",
    y = "Average Internet Usage Hours"
  )

@@

# use tidyverse-style code to pivot and summarise the data 
mean_income |> ggplot(aes(x = variable, y = value)) + 
  geom_point() +
  theme(axis.text.x = element_text(angle = 45,hjust=1), 
        axis.line = element_line(colour = "black"),
        title = element_text(size = 12)) +
  labs(
    x = "Average Total Family Income",
    y = "Internet Usage Hours"
  )

@@

```{r}
#| label: fig-maritalandinternet
#| fig-cap: Average Weekly Total of Internet Use by Marital Status
#| echo: false
## Marital 
# use tidyverse-style code to pivot and summarise the data 
mean_marital |> ggplot(aes(x = variable, y = value)) + 
  geom_point() +
  theme(axis.text.x = element_text(angle = 45,hjust=1), 
        axis.line = element_line(colour = "black"),
        title = element_text(size = 12)) +
  labs(
    x = "Marital Status",
    y = "Average Internet Usage Hours"
  )
```
@fig-maritalandinternet displays the relationship between marital status and internet usage in 2016. In accordance with popular opinion, people who have never been married use the Internet the most. Most notably, people who are widowed use the Internet the least, perhaps due to the correlation between age and widowhood.

@@

# use tidyverse-style code to pivot and summarise the data 
mean_edu |> ggplot(aes(x = variable, y = value)) + 
  geom_point() +
  theme(axis.text.x = element_text(angle = 45,hjust=1), 
        axis.line = element_line(colour = "black"),
        title = element_text(size = 12)) +
  labs(
    x = "Highest Education Obtained",
    y = "Internet Usage Hours"
  )
```
@fig-degreeandinternet displays the relationship between highest level of education obtained by the respondent and internet usage in 2016. Those who have completed a less than high school degree use the internet the least.

@@

# use tidyverse-style code to pivot and summarise the data 
mean_happy |> ggplot(aes(x = variable, y = value)) + 
  geom_point() +
  theme(axis.text.x = element_text(angle = 45,hjust=1), 
        axis.line = element_line(colour = "black"),
        title = element_text(size = 12)) +
  labs(
    x = "Level of Happiness",
    y = "Average Internet Usage Hours"
  )
```

>>>>

# use tidyverse-style code to pivot and summarise the data 
mean_age |> ggplot(aes(x = variable, y = value)) + 
  geom_col() +
  theme(axis.text.x = element_text(angle = 45,hjust=1), 
        axis.line = element_line(colour = "black"),
        title = element_text(size = 12)) +
  labs(
    x = "Age Group",
    y = "Average Internet Usage Hours"
  )

@@

# use tidyverse-style code to pivot and summarise the data 
mean_sex |> ggplot(aes(x = variable, y = value)) + 
  geom_col() +
  theme(axis.text.x = element_text(angle = 45,hjust=1), 
        axis.line = element_line(colour = "black"),
        title = element_text(size = 12)) +
  labs(
    x = "Sex",
    y = "Average Internet Usage Hours"
  )

@@

# use tidyverse-style code to pivot and summarise the data 
mean_race |> ggplot(aes(x = variable, y = value)) + 
  geom_col() +
  theme(axis.text.x = element_text(angle = 45,hjust=1), 
        axis.line = element_line(colour = "black"),
        title = element_text(size = 12)) +
  labs(
    x = "Race",
    y = "Average Internet Usage Hours"
  )

@@

# use tidyverse-style code to pivot and summarise the data 
mean_income |> ggplot(aes(x = variable, y = value)) + 
  geom_col() +
  theme(axis.text.x = element_text(angle = 45,hjust=1), 
        axis.line = element_line(colour = "black"),
        title = element_text(size = 12)) +
  labs(
    x = "Average Total Family Income",
    y = "Internet Usage Hours"
  )

@@

```{r}
#| label: fig-maritalandinternet
#| fig-cap: Average Weekly Total of Internet Use by Marital Status
#| echo: false
## Marital 
# use tidyverse-style code to pivot and summarise the data 
mean_marital |> ggplot(aes(x = variable, y = value)) + 
  geom_col() +
  theme(axis.text.x = element_text(angle = 45,hjust=1), 
        axis.line = element_line(colour = "black"),
        title = element_text(size = 12)) +
  labs(
    x = "Marital Status",
    y = "Average Internet Usage Hours"
  )
```
@fig-maritalandinternet displays the relationship between marital status and internet usage in 2016. In accordance with popular opinion, people who have never been married use the Internet the most. Most notably, people who are widowed use the Internet the least, perhaps due to the correlation between age and widowhood.

@@

# use tidyverse-style code to pivot and summarise the data 
mean_edu |> ggplot(aes(x = variable, y = value)) + 
  geom_col() +
  theme(axis.text.x = element_text(angle = 45,hjust=1), 
        axis.line = element_line(colour = "black"),
        title = element_text(size = 12)) +
  labs(
    x = "Highest Education Obtained",
    y = "Internet Usage Hours"
  )
```
@fig-degreeandinternet displays the relationship between highest level of education obtained by the respondent and internet usage in 2016. Those who have completed a less than high school degree use the internet the least.

@@

# use tidyverse-style code to pivot and summarise the data 
mean_happy |> ggplot(aes(x = variable, y = value)) + 
  geom_col() +
  theme(axis.text.x = element_text(angle = 45,hjust=1), 
        axis.line = element_line(colour = "black"),
        title = element_text(size = 12)) +
  labs(
    x = "Level of Happiness",
    y = "Average Internet Usage Hours"
  )
```
